Manuscript title here

### 2023-08-30 manuscript.Rmd
Update manuscript.Rmd

Injury is still a major cause of death around the world, taking the lives of around 4,4 million people each year, almost 8% of all deaths[@World_Health_Organization_2021]. In the United States, trauma is the 4th leading cause of death among the general population and the leading cause for people between the ages of 1 and 44[@AAST_2020]. It is also an important cause hospitalization and morbitidity among all age groups, including seniors, and are responsible for an estimated 10% of all years lived with a disability globally.

>>>>

Injury is still a major cause of death around the world, taking the lives of around 4,4 million people each year, almost 8% of all deaths[@World_Health_Organization_2021]. In the United States, trauma is the 4th leading cause of death among the general population and the leading cause for people between the ages of 1 and 44[@AAST_2020]. It is also an important cause hospitalization and morbitidity among all age groups, including seniors, and are responsible for an estimated 10% of all years lived with a disability globally[@connolly_woo_lampron_perry_2018][@World_Health_Organization_2021].
